### 2023-03-05 main/chapter_2ljets.tex
postit 131: split figure, expand caption

\begin{figure}[tp]
\centering
\begin{subfigure}{0.46\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRHigh.png}
\caption{DR-High}
\end{subfigure}
\hfill
\begin{subfigure}{0.46\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRllbb.png}
\caption{DR-$\llbb$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.46\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRInt.png}
\caption{DR-Int}
\end{subfigure}
\hfill
\begin{subfigure}{0.46\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRLow.png}
\caption{DR-Low}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.46\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DROffShell.png}
\caption{DR-OffShell}
\end{subfigure}
\caption[
Pre-fit yields in discovery regions
]{%
Pre-fit yields in discovery regions.
Errors are statistical.
}
\label{fig:2ljets_disco_prefit}
\end{figure}

@@

Histograms of our five discovery regions are displayed in
Figure~\ref{fig:2ljets_disco_prefit}
with pre-fit backgrounds and statistical uncertainties only.
The unblinded data in this figure repeat the SR-High and SR-Low deficits
mentioned previously.
To make inferences from these data, it is necessary to assign honestly
uncertain background models; the next section tackles this crucial problem of
background modelling.

>>>>

\begin{figure}[tp]
\centering
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRHigh.png}
\caption{DR-High}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRllbb.png}
\caption{DR-$\llbb$}
\end{subfigure}
\caption[
Pre-fit yields in discovery regions in DR-High and DR-$\llbb$
]{%
Pre-fit yields in discovery regions in DR-High and DR-$\llbb$.
Errors are statistical.
These are single-bin histograms.
Background yields are stacked and filled by colour.
Signal yields appear as lines and would add to the backgrounds.
Unblinded data are appear in black in regions that observe more than zero
events.%
}
\label{fig:2ljets_disco_prefit_higher}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRInt.png}
\caption{DR-Int}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRLow.png}
\caption{DR-Low}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DROffShell.png}
\caption{DR-OffShell}
\end{subfigure}
\caption[
Pre-fit yields in discovery regions in DR-Int, DR-Low, and DR-OffShell
]{%
Pre-fit yields in discovery regions in DR-Int, DR-Low, and DR-OffShell.
Errors are statistical.
These are single-bin histograms.
Background yields are stacked and filled by colour.
Signal yields appear as lines and would add to the backgrounds.
Unblinded data are appear in black in regions that observe more than zero
events.%
}
\label{fig:2ljets_disco_prefit_lower}
\end{figure}

@@

Histograms of our five discovery regions are displayed in
Figures~\ref{fig:2ljets_disco_prefit_higher}
and~\ref{fig:2ljets_disco_prefit_lower}
with pre-fit backgrounds and statistical uncertainties only.
The unblinded data in these figures repeat the SR-High and SR-Low deficits
mentioned previously.
To make inferences from these data, it is necessary to assign honestly
uncertain background models; the next section tackles this crucial problem of
background modelling.
